### 2019-12-19 R/msBalance.Rmd
updated structures

---
title: "msBalance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msBalance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Locate the Matlab source files.

```{r}
```

>>>>

---
title: "Balance responses in MS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msBalance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
source("../paths.txt")
```

## Locate sources
Reading source files from `r dataDir`

## Run Matlab code to load data

### 2019-12-19 README.Rmd
updated structures

1. Be sure to have `devtools` installed.
1. Use RStudio to create a local copy in `~/tmp` based on https://github.com/jlucasmckay/msBalance
    1. In RStudio, start a new Project: `File > New Project > Version Control > Git`
    1. In the “repository URL” paste: https://github.com/jlucasmckay/msBalance
    1. On OS X, make under `tmp`
    1. Click “Create Project” to create a new directory, which will be:
        * A directory/folder under `tmp`
        * A Git repository, linked to the remote GitHub repository
        * An RStudio Project
    1. If there are files that need to be added to the remote, they can be placed in this folder or dragged / dropped into the GitHub interface.
1. Edit vignettes/msBalance.Rmd and R files in R/.
1. Stage changed files, commit, and push changes with the git panel.

### Installing from GitHub for use
1. `devtools::install_github("jlucasmckay/msBalance", build_vignettes = TRUE)`
1. `vignette("msBalance")`

>>>>

1. Be sure to have `devtools` installed.
1. Use RStudio to create a local copy in `~/tmp` based on https://github.com/jlucasmckay/msBalance
    1. In RStudio, start a new Project: `File > New Project > Version Control > Git`
    1. In the “repository URL” paste: https://github.com/jlucasmckay/msBalance
    1. On OS X, make under `tmp`
    1. Click “Create Project” to create a new directory, which will be:
        * A directory/folder under `tmp`
        * A Git repository, linked to the remote GitHub repository
        * An RStudio Project
    1. If there are files that need to be added to the remote, they can be placed in this folder or dragged / dropped into the GitHub interface.
1. Path locations (used by R and Matlab code) are in paths.txt
1. The main analysis is in R/msBalance.Rmd
1. Stage changed files, commit, and push changes with the git panel.

### Navigating a mixture of Matlab and R code

The source files are in .mat format.
There is a mixture of matlab preprocessing code (files in m/) into .csv files that R can then read (files in R/).
A directory csv/ is created to hold these files.
The contents of this directory are ignored by git so that these files are not automatically loaded to GitHub.
